Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-22 paper/paper.tex
Updated figures for pareto ensembles, cleanup unused figures
added abstract, related work and affiliation

\numberofauthors{2}
\author{
    \alignauthor Maciej Malawski and Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{Center for Research Computing}\\
       \affaddr{111 Information Technology Center}\\
       \affaddr{Notre Dame, IN, USA}\\
       \email{\{mmalawsk,naber\}@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{4676 Admiralty Way}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
}

@@

\begin{abstract}
Abstract goes here.
\end{abstract}

@@

@@

(a) Number of workflows completed $N_c$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   57  & 45 &  18 &  14  &  0 & 134\tabularnewline
WA-DPDS   &    96 &  87  & 48  & 34  &  0 & 265\tabularnewline
SPSS     &    29  & 42  & 192  & 74  & 50 & 387\tabularnewline
\end{tabular}
\medskip

(b) Total amount of computing time completed $T_C$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip

>>>>

\numberofauthors{3}
\author{
    \alignauthor Maciej Malawski\\
       \affaddr{AGH University of Science and Technology}\\
       \affaddr{Dept. of Computer Science}\\
       \affaddr{Krakow, Poland; and}\\
       \affaddr{University of Notre Dame}\\
       \affaddr{Center for Research Computing}\\
       \affaddr{111 ITC, Notre Dame, IN, USA}\\
       \email{mmalawsk@nd.edu}
    \alignauthor Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{Center for Research Computing}\\
       \affaddr{111 ITC, Notre Dame, IN, USA}\\
       \email{naber@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{4676 Admiralty Way}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
}

@@

\begin{abstract}

Large-scale computational applications represented as scientific workflows, are
often grouped into ensembles composed of several inter-related workflows. In
this paper, we address a new important problem of maximizing the number of
completed workflows from an ensemble under both budget and deadline constraints
on the Infrastructure-as-a-Service (IaaS) clouds, characterized by dynamic
resource provisioning capabilities and pay-per-use model.  We discuss, develop
and assess algorithms based on static and dynamic strategies for both task
scheduling and resource provisioning. We evaluate the algorithms via simulation
using a set of scientific workflow ensembles with a broad range of budget and
deadline parameters. This allows to identify the application scenarios and
constraint ranges for which the algorithms perform better. We found that the key
for algorithm performance is the decision which workflows should be admitted or
rejected from the ensemble. The results show that the admission procedure based
on worklfow structure and estimates of task runtimes can significantly improve
the quality of solutions.

\end{abstract}

@@

The main contributions of this paper are:
\begin{itemize}
  \item definition of the scheduling problem of priorotized workflows grouped in
  ensembles, under both budget and deadline constraints,
  \item analysis of static and dynamic strategies for task scheduling and
  resource provisioning on clouds, together with the admission procedure to
  predict which workflows from the ensemble can be completed,
  \item development of static and dynamic algorithms and of the simulator based
  on the defined application and infrastructure model,
  \item performance evaluation of algorithms on the set of synthetic benchmark
  workflow ensembles representing important real scientific applications,
  \item analysis of results, which allows to assess the advantages and
  disadvantages of proposed algorithms, depending on application scenarios and
  varying constraint values.
\end{itemize}

@@

(a) Number of workflows completed $N_c$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &    55 &  47  & 23  & 14  &  0 & 139\tabularnewline 
WA-DPDS   &    97 &  89  & 50  & 34  &  1 & 271\tabularnewline 
SPSS      &    38 &  37  & 190 & 74  & 50 & 389\tabularnewline
\end{tabular}
\medskip

(b) Total amount of computing time completed $T_C$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   55  & 47  &  26  & 14  &  0 & 142\tabularnewline
WA-DPDS   &   96  & 98  &  59  & 26  & 10 & 289\tabularnewline
SPSS      &   32  & 12  & 165  & 75  & 41 & 325\tabularnewline
\end{tabular}
\medskip

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   55  & 47  &  26  & 14  &  0 & 142\tabularnewline
WA-DPDS   &   96  & 98  &  59  & 26  & 10 & 289\tabularnewline
SPSS      &   32  & 12  & 165  & 75  & 41 & 325\tabularnewline
\end{tabular}
\medskip
